Rotations and Insecticide Resistance initial plots

### 2017-10-05 inst/documents/rotations1.Rmd
fixed setting exposures differently for each insecticide
starting to allow fitnesses to be set properly

@@

dfr <- run_rot(rotation_interval=50, max_generations = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, migration_rate_intervention=0.01)

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hold', fig.align='left', fig.cap="Rotation interval 50, migration 0.001"}

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hold', fig.align='left', fig.cap="Rotate when resistant, migration 0.001"}

### Rotate when resistant, migration 0.001

dfr <- run_rot(rotation_interval=0, max_generations = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, migration_rate_intervention=0.001)

>>>>

# Current state of play

1. Flexible number of insecticides between 1 & 5
1. Exposure can be set for each insecticide or same for all.
1. Starting frequency can be set for each insecticide or same for all.

Some example plots follow, these act as a visual test that the model is doing what we expect.

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hold', fig.align='left', fig.cap="exposure set to 1 for r1 and 0.1 for r2"}

#expo_hi=c(1,0.1)
dfr <- run_rot(n=2, rotation_interval=100, expo_hi=c(1,0.1))

@@

# TODO remove hardcode fitnesses from here
dfr <- run_rot(rotation_interval=50, max_generations = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, migration_rate_intervention=0.01)

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hold', fig.align='left', fig.cap="decrease migration to 0.001"}

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hold', fig.align='left', fig.cap="cost 0.1 effectiveness 1"}
dfr <- run_rot(n=3, rotation_interval=50, eff=1, cost=0.1)
```

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hold', fig.align='left', fig.cap="Rotate when resistant, exposure 0.5 migration 0.01"}

### Rotate when resistant, migration 0.01

dfr <- run_rot(rotation_interval=0, max_generations = 300, hardcode_fitness = TRUE, same_insecticides =TRUE, expo_hi=0.5, migration_rate_intervention=0.01)

### 2017-10-05 inst/documents/rotations_notes.Rmd
starting to allow fitnesses to be set properly

>>>>

I now have run_rot() working for flexible numbers of insecticides (1-5).

done : Next, get active and refuge onto the same plots.  
done : allowed starting frequencies to be set

implemented set_expsoure_rot() now working
dfr <- run_rot(rotation_interval=50, expo_hi=0.9)
dfr <- run_rot(rotation_interval=50, expo_hi=0.2)
# diff frequency curves for r1 & r2
dfr <- run_rot(n=2, rotation_interval=50, expo_hi=c(1,0.1))

started fitness_single_locus() from run_rot()

dfr <- run_rot(n=2, rotation_interval=50, eff=c(1,0.1))

# TODO
~ test fitness_single_locus() from run_rot() and add to Rmd

~ test setting inputs correctly (move away from hardcoded test functions)
~ find what went wrong when I set fitnesses
~ get Ian to pull changes

# state of play
~ rotations1.Rmd : example plots
